The seed germination spectrum of alpine plants: a global meta-analysis

### 2020-09-14 doc/manuscript.Rmd
1st submission 🍋

---
title: "The global seed germination spectrum of alpine plants"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

We conducted a meta-analysis of primary data [@RN4734], which consists of pooling together original data from different local studies to synthesize their conclusions at the global level. The original data files, as well as R code for data cleaning, analysis and manuscript production are available at https://github.com/efernandezpascual/alpineseeds. To gather data, we contacted research groups which have performed experiments on seed germination of alpine plants, asking them to provide raw data from laboratory germination experiments. The submitted data had to report the studied species, the germination treatments, the number of seeds sown, and the number of seeds germinated. We received data (Table 1) from the Cantabrian Mountains of Spain, the European Alps, the Italian Apennines, the Northern Caucasus, the Qinghai-Tibet Plateau of China, the Chilean Andes, and the Australian Alps. We also received data on European alpine species from *Enscobase*, the database of the European Native Seed Conservation Network (http://enscobase.maich.gr/index.tml).

@@

Once received, we standardized the species names according to *The Plant List* [@RN2321] using the package *Taxonstand* [@RN4660] in *R* [@RN2315]. For each species, we recorded its elevation range from local floras [@RN4741; @RN4739; @RN3243; @RN4742; @RN4740], catalogues [@RN4738] and herbaria (*Australian National Herbarium*, https://www.anbg.gov.au/cgi-bin/anhsir). We used the elevation ranges (i) to remove from the dataset outlier species that do not grow above the treeline; and (ii) to classify the rest of the species as *strict alpine* (i.e. species that only grow above the treeline) or *generalist* (i.e. species that can grow above the treeline but also in the lowlands). For each species, we compiled three additional traits. First, seed dormancy class obtained from Baskin & Baskin [-@RN3214] and Rosbakh et al. [-@RN4743]. We simplified the original dormancy classes to five categories: physiological (germination prevented by the seed’s internal balance of phytohormones), morphological (germination prevented by an embryo which is underdeveloped at the time of dispersal), morphophysiological (both physiological and morphological dormancy present), physical (germination prevented by a water-impermeable seed coat) or non-dormant. Second, seed mass as provided by the Royal Botanic Gardens Kew Seed Information Database [-@RN2987] and some additional sources [@RN4728; @RN4735; @RN3376]. Third, the embryo to seed surface ratio. Embryo to surface area values were based on measurements of the surface area of the embryo and seed from drawings and photographs retrieved mainly from Martin [-@RN3244] and the Royal Botanic Gardens Kew Seed Information Database [-@RN2987], supplemented with own measurements (Vandelook, unpublished). For some species that were missing seed mass or embryo values, we calculated genus or family averages.

@@

The original data, R code for the analysis and creation of the manuscript can be accessed at the GitHub repository https://github.com/efernandezpascual/alpineseeds. Upon publication, a version of record of the repository will be deposited in Zenodo.

@@

```{r fig2, message = FALSE, echo = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "Effect of the germination environment on germination, according to the MCMC meta-analysis of the primary data. The dots indicate the posterior mean of the effect size, and the brackets its 95 % credible interval. The line of zero effect is shown. When the credible intervals overlap with the zero-effect line, the effect is not significant. The figure shows first the main effect, then the effects for the strict alpine and generalist groups, and then the interaction with seed mass and embryo:endosperm. A negative interaction (e.g. seed mass and light, in the case of the germination proportion) indicates that, as the interacting factor increases (e.g. seed mass) the response to the germination cue (e.g. light) decreases, in comparison with the main effect.", fig.align = "center", fig.width=7, fig.height=5.5}
cowplot::ggdraw(fig2)
```

>>>>

---
title: "The seed germination spectrum of alpine plants: a global meta-analysis"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

We conducted a meta-analysis of primary data [@RN4734], which consists of pooling together original data from different local studies to synthesize their conclusions at the global level. All data processing, analysis and manuscript production has been performed in *R* [@RN2315]. The original data, plus R code for the analysis and creation of the manuscript using Rmarkdown, can be accessed at the GitHub repository https://github.com/efernandezpascual/alpineseeds. (The repository will be made open when the manuscript is accepted for publication, a zip version has been uploaded to https://drive.google.com/file/d/12Usqi7fOAbOoZ9Uu9wkJt2FANB629LFP/view?usp=sharing for peer-review). To gather data, we contacted research groups which have performed experiments on seed germination of alpine plants, asking them to provide raw data from laboratory germination experiments. The submitted data had to report the studied species, the germination treatments, the number of seeds sown, and the number of seeds germinated. We received data (Table 1) from the Cantabrian Mountains of Spain, the European Alps, the Italian Apennines, the Northern Caucasus, the Qinghai-Tibet Plateau of China, the Chilean Andes, and the Australian Alps. We also received data on European alpine species from *Enscobase*, the database of the European Native Seed Conservation Network (http://enscobase.maich.gr/index.tml).

@@

Once received, we standardized the species names according to *The Plant List* [@RN2321] using the package *Taxonstand* [@RN4660] in *R*. For each species, we recorded its elevation range from local floras [@RN4741; @RN4739; @RN3243; @RN4742; @RN4740], catalogues [@RN4738] and herbaria (*Australian National Herbarium*, https://www.anbg.gov.au/cgi-bin/anhsir). We used the elevation ranges (i) to remove from the dataset outlier species that do not grow above the treeline; and (ii) to classify the rest of the species as *strict alpine* (i.e. species that only grow above the treeline) or *generalist* (i.e. species that can grow above the treeline but also in the lowlands). For each species, we compiled three additional traits. First, seed dormancy class obtained from Baskin & Baskin [-@RN3214] and Rosbakh et al. [-@RN4743]. We simplified the original dormancy classes to five categories: physiological (germination prevented by the seed’s internal balance of phytohormones), morphological (germination prevented by an embryo which is underdeveloped at the time of dispersal), morphophysiological (both physiological and morphological dormancy present), physical (germination prevented by a water-impermeable seed coat) or non-dormant. Second, seed mass as provided by the Royal Botanic Gardens Kew Seed Information Database [-@RN2987] and some additional sources [@RN4728; @RN4735; @RN3376]. Third, the embryo to seed surface ratio. Embryo to surface area values were based on measurements of the surface area of the embryo and seed from drawings and photographs retrieved mainly from Martin [-@RN3244] and the Royal Botanic Gardens Kew Seed Information Database [-@RN2987], supplemented with own measurements (Vandelook, unpublished). For some species that were missing seed mass or embryo values, we calculated genus or family averages.

@@

The original data, R code for the analysis and creation of the manuscript can be accessed at the GitHub repository https://github.com/efernandezpascual/alpineseeds. Upon publication, a version of record of the repository will be deposited in Zenodo. (The repository will be made open when the manuscript is accepted for publication, a zip version has been uploaded to https://drive.google.com/file/d/12Usqi7fOAbOoZ9Uu9wkJt2FANB629LFP/view?usp=sharing for peer-review)

@@

```{r fig2, message = FALSE, echo = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "Effect of the germination environment on germination, according to the MCMC meta-analysis of the primary data. The dots indicate the posterior mean of the effect size, and the brackets its 95 % credible interval. The line of zero effect is shown. When the credible intervals overlap with the zero-effect line, the effect is not significant. The figure shows first the main effect, then the effects for the strict alpine and generalist groups, and then the interaction with seed mass and embryo:seed. A negative interaction (e.g. seed mass and light, in the case of the germination proportion) indicates that, as the interacting factor increases (e.g. seed mass) the response to the germination cue (e.g. light) decreases, in comparison with the main effect.", fig.align = "center", fig.width=7, fig.height=5.5}
cowplot::ggdraw(fig2)
```
